---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

`instevalR` is an R package under construction that is useful for people doing course evaluations (at universities, e.g., U Mannheim) with the software InstEvaL (https://insteval.uni-mannheim.de). The package has functions to combine the results of multiple course evaluations (e.g., different courses/cohorts of a single instructor) and to plot those results:

```{r, example-plot, echo = F, eval = T, dpi=300}
library("instevalR")
set.seed(123456)
dat.x <- sim_eval(N.files = 5, N.id = 100)
res.x <- aggregate_eval(dat.x)
plot_eval(res.x, ylim = c(1, 3))
```

In order to use this package, you need three things:

1.  The *.csv-files of your course evaluations, which you can downlaod from InstEvaL (InstEvaL -> Results -> Raw data). Please save all your *.csv-files in a single directory.
2.  R (which you can download from http://www.r-project.org)
3.  The package `instevalR`

The easiest way to install the package `instevalR` is to install it directly from GitHub:
```{r, echo = T, eval = F}
# install "devtools" unless you already have it, may take 1 or 2 minutes
install.packages("devtools")
devtools::install_github("hplieninger/instevalR")
```

After you have your *.csv-files, R, and the package, you can get started:
```{r, echo = T, eval = F}
library("instevalR")                               # load in every new R session
dat.1 <- read_eval("path/to/directory")            # read-in raw data
res.1 <- aggregate_eval(dat.1)                     # combine into single object
plot_eval(res.1)                                   # do a plot
```

If you don't have *.csv-files (yet) or just want to explore the package, you may do this using simulated data:
```{r, echo = T, eval = F}
library("instevalR")                               # load in every new R session
dat.1 <- sim_eval()                                # simulate raw data
res.1 <- aggregate_eval(dat.1)                     # combine into single object
plot_eval(res.1)                                   # do a plot
```

Happy teaching. Please send any bug reports, feature requests, or comments to `plieninger@uni-mannheim.de` (in English or German).

*****

This R package was developed independently from the official InstEvaL project. The author of this R package is in no way affiliated with InstEvaL, there is no conflict of interests, no money, no beer, nothing. Just for fun.
